Zonotoop--a large scale aggregating data warehouse for time-series-based data. [DRAFT]

### 2009-05-05 doc/report/msc-report.tex
contents rearrangement and minor additions.

@@

@@

TODO

URLParser

Client

Data

Transform

OHM is built upon existing tools and software. It uses Apache Hadoop and
HBase, free implementations of Googles' MapReduce and BigTable
respectively, both implemented in Java.

and the user 
JSON\footnote{JavaScript Object Notation} is transported over a RESTful
interface or data is transported with Thrift.

The user's datasets are defined using YAML--a human friendly data
serialization standard. The datasets reside in the config directory.

\subsection{Input and output formats}

>>>>

\subsection{Column-qualifiers}

@@

\chapter{Theory [TODO: needs better name]}

\section{Time-series}

\section{Multidimensional arrays}

\subsection{Data cubes}

\subsection{Cube lattice}

\section{Projections}

\section{Granularity}

\chapter{Tools}

\section{Python}

\subsection{Paste}

\subsection{PyYAML}

\subsection{Setuptools}

\subsection{simplejson}

OHM is built upon existing tools and software. It uses Apache Hadoop and
HBase, free implementations of Google's MapReduce and BigTable
respectively, both implemented in Java.

JSON\footnote{JavaScript Object Notation} is transported over a RESTful
interface or data is transported with Thrift.

The user's datasets are defined using YAML--a human friendly data
serialization standard. The dataset files reside in the config directory.

\section{Importing}

The user defines a mapper which OHM wraps, interpreting the output from the
mapper program and storing it in HBase.

Support exists for writing the mapper in Java or Python.

\subsection{Input formats}

\subsection{Output formats}

\subsubsection{Darling}

@@

Built with Python Paste--a middleware framework--the data server dispatches
to the requested application depending on the URI it was fed.

\section{URLParser}

Dispatching.

\section{Clients}

Dispatches to static files in client directory in the project directory.
Custom clients can be built with HTML and JavaScript, see the examples.

\section{Data}

Serves data from HBase, dumps it as JSONP.

\section{Transformers}

Fetches data from HBase and transforms it with the requested transform
program in the transformers directory in the project directory, output is
dumped as JSONP.
